legacy effects

### 2018-12-10 analysis/legacy_effects.Rmd
add legacy years

```{r}
# Boostrap Confidence Intervals

@@

>>>>

```{r}
# Boostrap Confidence Intervals 
set.seed(1234)

@@

```{r}
ylegacy <- legacy %>% 
  filter(!(year %in% seq(2005+1, 2005+6, by=1))) %>% 
  filter(!(year %in% seq(2012+1, 2012+6, by=1))) %>% 
  group_by(ypd) %>%
  summarise(mean=mean(lag, na.rm=T),
            sd = sd(lag, na.rm=T),
            se = sd/sqrt(length(lag))) %>% 
  mutate(d = "all")

ly2005 <- legacy %>%
  filter(year %in% seq(2005+1, 2005+6, by=1)) %>% 
  dplyr::select(-site) %>% rename(site = site_sorted) %>% 
  group_by(ypd) %>%
  summarise(mean=mean(lag, na.rm=T),
            sd = sd(lag, na.rm=T),
            se = sd/sqrt(length(lag))) %>% 
  mutate(d = "2005")

ly2012 <- legacy %>%
  filter(year %in% seq(2012+1, 2012+6, by=1)) %>% 
  dplyr::select(-site) %>% rename(site = site_sorted) %>% 
  group_by(ypd) %>%
  summarise(mean=mean(lag, na.rm=T),
            sd = sd(lag, na.rm=T),
            se = sd/sqrt(length(lag))) %>% 
  mutate(d = "2012")

ly <- rbind(ylegacy, ly2005, ly2012)

p2 <- ly %>% ggplot(aes(x = ypd, y = mean)) + 
  # geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill=site), alpha=.5) + 
  geom_line(aes(colour=d)) + 
  geom_point(aes(colour=d), size=3) + 
  geom_errorbar(data = (dplyr::filter(ly, d == "all") %>% as.data.frame()), 
                aes(ymin=mean - se, ymax = mean + se, colour = d), width = 0.2) + 
  theme_bw() + 
  geom_hline(yintercept = 0, colour = 'black') + 
  theme(panel.grid = element_blank(), 
        strip.background = element_blank()) +  
  scale_x_continuous("Years post drougth event", breaks=c(1:6)) + 
  scale_y_continuous("Observed - Predicted Growth", breaks=seq(-0.4, 0.2, by=0.05))

pdf(here::here('/out/legacy', 'legacy_droughts_2005_2012.pdf'), width=8, height = 5)
p2
dev.off()
